\documentclass[]{article}
\usepackage{xcolor}
\begin{document}
\begin{center}
\phantom{Mumbai}
\vspace{3 em}

{\LARGE Smells Like Teen Spirit}

\vspace{1.5 em}{\large Nirvana 

\vspace{0.9 em} 1991}
\end{center}
\vspace{1.5 em} And I forget just why I taste, oh yeah, I guess it makes me smile.
\\I find it hard, it’s hard to find,

{\raggedleft \textit{Oh well, whatever, \\ \hspace{28.7 em} nevermind.}}

\vspace{1.3 em}

\noindent\textbf{Hello, hello, hello, how low
\\ Hello, hello, hello, how low
\\ Hello, hello, hello, how low
\\ Hello, hello, hello
}

\vspace{3 em}
\noindent\textbf{\textit{With the lights out it’s less \textcolor{red}{dangerous},
\\ Here we are now, entertain us,
\\ \textcolor{brown!20!violet!10!red!60!black}{I feel stupid and contagious,}
\\ Here we are now, entertain us!
}}

\vspace{0.4 em}
\begin{center}
\hspace{5 em}\textbf{A \textcolor{brown!50!black}{\underline{mulatto}}! An \textcolor{white!60!black}{\underline{albino!}} A \underline{mosquito!} 
\textcolor{violet!64!black}{My libido!}}

\vspace{4 em}
\textsc{{\hspace{0.5 em}\large A denial! A denial! A denial!}
\vspace{1 em}
\\\hspace{1 em}\LARGE{A denial! A denial! A denial!}
\vspace{1 em}
\\\huge{A denial! A denial! A denial!}
}
\end{center}
\newpage
\begin{description}
\item [Name] Atishay Jain. It means ``extreme" or ``to an extremely great extent".
\item [Department] Computer Science and Engineering
\item [Music] I like evergreen, beautiful and joyful music. Some of my favourites are:
\begin{itemize}
    \item Neele Neele Ambar Par (Kishore Kumar)
    \item O Mere Dil Ke Chain (Kishore Kumar)
    \item Sochta Hoon (Nusrat Fateh Ali Khan)
\end{itemize}
\end{description}
\end{document}